\pagebreak
\section{GDS 2.0 Document Management Policy}
The purpose of a GDS document management Policy is to establish the framework under which
official records and documents of GHRSST are created and managed. It lists the responsibilities of
key actors, and articulates the principles underpinning the processes outlined in the records and
document management guidelines.
\newp

The \textbf{intent} of this Policy is to ensure that the GHRSST GPO, Science Team and actors working
within GHRSST have the appropriate governance and supporting structure in place to enable them to
manage their records and documents in a manner that is planned, controlled, monitored, recorded
and audited, using an authorized system.
This Policy states the key strategic and operational requirements for adequate recordkeeping and
document management of the GDS to ensure that evidence, accountability and information about
GHRSST activities are met.
\newp

The \textbf{scope} of this Policy is applicable to all people working in GHRSST and to all official records and
documents, in any format and from any source. Examples include paper, electronic messages, digital
documents and records, video, DVD, web-based content, plans, and maps. This Policy does not
apply to public domain material.
\newp 

\subsection{GDS Document Management Definitions}
\begin{longtable}{|p{0.2\textwidth}|p{0.4\textwidth}|}
    \label{tab:gds_document_definitions} \\
    \hline \endhead \hline \endfoot
    \textbf{Document: } & Structured units of information recorded in any
    format and on any medium and managed as discrete units or objects. Some documents are records because they have participated in a business transaction, or were created to document such a transaction. Conversely, some documents are not records because they do not function as evidence of a business transaction. \\ \hline
    \textbf{Email: } & The transmission of text messages and optional file attachments over a network. \\ \hline 
    \textbf{ERDMS: } & Electronic Records and Document Management System. \\ \hline 
    \textbf{Records:} & Information created, received, and maintained as evidence and information by an organization or person, in pursuance of legal obligations or in the transaction of business. \\ \hline
    \textbf{Records Management:} & Field of management responsible for the efficient and systematic control of the creation, receipt, maintenance, use and disposition of records, including processes for capturing and maintaining evidence of and information about business activities and transactions in the form of records.\\ 
\end{longtable}

\subsection{GDS Document Management Policy Statement}
GDS records and documents created, received or used by GHRSST in the normal course of activities
are the property of the GHRSST project, unless otherwise agreed. This includes reports compiled by
external consultants commissioned by the GHRSST Project Office or Science Team. 
\newp

GHRSST official records constitute its corporate memory, and as such are a vital asset for ongoing
operations, and for providing evidence of activities and transactions. They assist the GPO and GHRSST Science Team in making better informed decisions and improving best practice by providing an accurate record of what has occurred before.
\newp

Thus GDS records are to be: 
\setlist{nolistsep}
\begin{itemize}[noitemsep]
    \item managed in a consistent and structured manner;
    \item managed in accordance with best practice guidelines and procedures;
    \item stored in a secure manner.
    \item disposed of, or permanently archived appropriately;
    \item captured and registered using an authorized recordkeeping system
\end{itemize}
\newp

GHRSST GDS documents are to be
\setlist{nolistsep}
\begin{itemize}[noitemsep]
    \item created by authorized officers and managed by the GPO
    \item version controlled by authorized officers 
\end{itemize}

\subsection{GDS Document Management Policy Responsibility}
The GHRSST Science Team is responsible for GDS Records Management and has delegated responsibility for records management to the GPO coordinator.
\newp

The Coordinator is accountable for providing assistance in the overall management of the GDS and documents, including:
\begin{itemize}[noitemsep]
    \item  management of the GHRSST Document Management System (GHRSST Website document repository);
    \item providing assistance on the implementation and interpretation of the GDS Document Management;
    \item maintaining and developing GHRSST GDS document Management policy and promulgating this across GHRSST as a whole;
    \item identifying retention and disposal requirements for GHRSST records;
    \item providing training in GDS document management processes and the GHRSST website document repository
\end{itemize}

\subsection{GHRSST GDS Recordkeeping and Document
Management System}
The GHRSST recordkeeping and document management system assists people working in GHRSST
to capture records, protect their integrity and authenticity, provide access through time, dispose of
records no longer required by GHRSST in the conduct of its activities, and ensure records of enduring
value are retained. It also facilitates the creation, version control, and authority of official corporate
documents.
\newp

The GHRSST recordkeeping and document management system is managed by the GPO which
provides ongoing support, development and training, so that GHRSST community responsibilities are met.
\newp

The GHRSST authorized recordkeeping and document management system is the GHRSST Project
Office Web site document library (\url{http://www.ghrsst.org}).
\newp

All GHRSST actors are to use \url{http://www.ghrsst.org} to ensure that:
\setlist{nolistsep}
\begin{itemize}[noitemsep]
    \item GDS official records and documents are routinely captured and subjected to the relevant retention and disposal policy;
    \item access to records and documents is managed according to authorized access and appropriate retention times regardless of international location;
    \item records and documents are protected from unauthorized alteration or deletion;
    \item documents are version controlled as required;
    \item there is one authoritative and primary source of information documenting GHRSST GDS decisions and actions.
\end{itemize}
\newp

All GHRSST actors who create, receive and keep records and documents as part of their GHRSST
work, should do so in accordance with these policies, procedures and standards. GHRSST actors
should not undertake disposal of records without the authority of the GPO – and only in accordance
with authorized disposal schedules.
%\newp

\subsection{GDS Document location}
\begin{enumerate}[noitemsep]
    \item An approved and complete version of the GDS shall be stored on the GHRSST web site (\url{http://www.ghrsst.org}) under the documents -> GDS -> operational section of the web site. This version shall be the Operational version of the GDS.
    \item A development version of the GDS shall be stored on the GHRSST web site (\url{http://www.ghrsst.org}) under the documents -> GDS -> development section of the web site. This version shall be the development version of the GDS
    \item An archive of all GDS documents shall be stored on the GHRSST web site (\url{http://www.ghrsst.org}) under the documents -> GDS -> archive section of the web site.
    \item A single zip file containing all operational documents shall be available at the GHRSST web site
\end{enumerate}

\subsection{GDS Document Publication}
\begin{enumerate}[noitemsep]
    \item The GHRSST Project Office is responsible for publication of GDS operational documents
    \item A document BookCaptain is responsible for the publication of development GDS documents and shall inform the GHRSST project office when new documents have been published.
\end{enumerate}

\subsection{GDS Document formats}
\begin{enumerate}[noitemsep]
    \item Operational GDS documents shall be stored as pdf documents.
    \item Development GDS documents shall be stored as Microsoft word documents.
    \item Both word and pdf documents shall be stored in the GDS archive.
\end{enumerate}

\subsection{GDS Document filing}
\begin{enumerate}[noitemsep]
\item Documents shall be numbered using the following nomenclature suffix to be appended at the end of a filename : \newp
MM.mmm \newp
where MM is the major revision e.g. 2 and mmm is a minor revision e.g. 019. for example, the
following GDS filename is valid \newp
GDS2.0\_TechnicalSpecifications\_rev02.001.doc \newp 
\item Following any change to a document, a new revision number shall be assigned to the document by the BookCaptain before publication.
\end{enumerate}

\subsection{Document retrieval}
\begin{enumerate}[noitemsep]
\item Free and open access to all GDS documents shall be provided by the GHRSST web page interface.
\end{enumerate}

\subsection{Document security}
\begin{enumerate}[noitemsep]
\item GDS documents stored within the GHRSST web page are backed up by the web hosting company every night.
\item An independent backup copy of all GDS documents shall be maintained by the GHRSST Project Office.
\end{enumerate}

\subsection{Retention and long term archive}
\begin{enumerate}[noitemsep]
\item GDS documents shall be retained in perpetuity within a stewardship facility.
\end{enumerate}

\subsection{Document workflow}
\begin{enumerate}[noitemsep]
\item Each GDS document shall be owned and administered by a document Book Captain.
\item A GDS BookCaptain is a central point of contact that is responsible for managing and maintaining the content of their GDS document
\item All revisions must be approved by a GDS document Book Captain.
\item All updates and revisions shall be entered into the Document change record.
\item A revised version of the GDS is the passed to the GPO coordinator for registration and document management (revision control).
\item A revised version of the GDS is the passed by the GPO to the GHRSST Data and Systems Technical Advisory Group (DAS-TAG) for review.
\item If required, the GPO may convene an external review Board to subject the revised GDS document to an independent peer review.
\item Proposed changes to the GDS, as provided by the DAS-TAG (and independent peer review if convened) are passed back to the Book Captains for implementation.
\item A final version of the GDS documents is passed back to the GPO.
\item A final version of the GDS is passed to the GHRSST Advisory council for approval.
\item The GPO publishes the GDS document on the GHRSST web site in the appropriate location of the GHRSST document library.
\end{enumerate}

\subsection{Document creation}
\begin{enumerate}[noitemsep]
    \item The GHRSST Project Office, in collaboration with the GHRSST Science Team is responsible for the creation of new GDS documents.
    \item The GHRSST Project Office may delegate the responsibility to create new documents to a member of the GHRSST Science Team.
\end{enumerate}